Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-13 R0V0.tex
Item 26. Implementing new example
Item 26. Done implementing the chordal graph case for the new example

\section{Numerical Experiment}\label{sec:Illustration}

@@

\mypara The graph describing the network structure in provided in Figure~\ref{fig:cycle graph}.
\begin{figure}[htpb!]
	\centering
	\input{./imgs/CyclicGraph.pdf_tex}
	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
	\label{fig:cycle graph}
\end{figure}

@@

\mypara The graph describing the network structure in provided in Figure~\ref{fig:graph}.
\begin{figure}[htpb!]
	\centering
	\input{./imgs/GraphStructure.pdf_tex}
	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
	\label{fig:graph}
\end{figure}

\mypara The matrix $W$ obtained is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.72,0.19)$. The matrix $Y$ is given by
\begin{equation*}
	Y(q)=\begin{bmatrix}
		\underline{Y}(q_1,\breve{q}_1)&\overline{Y}(q_1,\breve{q}_1)&0_{2\times1}&\overline{Y}(q_1,\breve{q}_1)\\
		\overline{Y}(q_2,\breve{q}_2)&\underline{Y}(q_2,\breve{q}_2)&\overline{Y}(q_2,\breve{q}_2)&0_{2\times1}\\
		0_{2\times1}&\overline{Y}(q_3,\breve{q}_3)&\underline{Y}(q_3,\breve{q}_3)&\overline{Y}(q_3,\breve{q}_3)\\
		\overline{Y}(q_4,\breve{q}_4)&0_{2\times1}&\overline{Y}(q_4,\breve{q}_4)&\underline{Y}(q_4,\breve{q}_4)
	\end{bmatrix}\;,
\end{equation*}
where $\underline{Y}(q_i,\breve{q}_i)=-2.26\begin{bmatrix}y_i,&y_i^2+x_i^2+\sum_{j\in\mathscr{N}(i)}y_j^2+x_j^2\end{bmatrix}$,
$\overline{Y}(q_i,\breve{q}_i)=\begin{bmatrix}0.002y_i,0\end{bmatrix}$ and $0_{2\times1}$ stands for the vector $[0,0]\in\mathbb{R}^2$.

@@

>>>>

\section{Numerical Experiments}\label{sec:Illustration}

@@

@@

\mypara The graph describing the network structure in provided in Figure~\ref{fig:graph}. Consider the case with $N=4$.

\begin{figure}[htpb!]
	\centering
	\input{./imgs/GraphStructure.pdf_tex}
	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
	\label{fig:graph}
\end{figure}

@@

\mypara Consider the with four agents (i.e., $N=4$) network having the topology illustrated in Figure~\ref{fig:cycle graph}.

\begin{figure}[htpb!]
	\centering
	\input{./imgs/CyclicGraph.pdf_tex}
	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
	\label{fig:cycle graph}
\end{figure}

\mypara In the ``neighbour'' case, the solver took 11.7s to solve the MI~\eqref{eq:MI formulation} using chordal graphs. The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.72,0.19)$. The matrix $Y$ is given by
\begin{equation*}
	Y(q)=\begin{bmatrix}
		\underline{Y}(q_1,\breve{q}_1)&\overline{Y}(q_1,\breve{q}_1)&0_{2\times1}&\overline{Y}(q_1,\breve{q}_1)\\
		\overline{Y}(q_2,\breve{q}_2)&\underline{Y}(q_2,\breve{q}_2)&\overline{Y}(q_2,\breve{q}_2)&0_{2\times1}\\
		0_{2\times1}&\overline{Y}(q_3,\breve{q}_3)&\underline{Y}(q_3,\breve{q}_3)&\overline{Y}(q_3,\breve{q}_3)\\
		\overline{Y}(q_4,\breve{q}_4)&0_{2\times1}&\overline{Y}(q_4,\breve{q}_4)&\underline{Y}(q_4,\breve{q}_4)
	\end{bmatrix}\;,
\end{equation*}
where $\underline{Y}(q_i,\breve{q}_i)=-2.26\begin{bmatrix}y_i,&y_i^2+x_i^2+\sum_{j\in\mathscr{N}(i)}y_j^2+x_j^2\end{bmatrix}$,
$\overline{Y}(q_i,\breve{q}_i)=\begin{bmatrix}0.002y_i,0\end{bmatrix}$ and $0_{2\times1}$ stands for the vector $[0,0]\in\mathbb{R}^2$.

\mypara In the ``neighbour'' case, the solver took 5.7s to solve the MI~\eqref{eq:MI formulation} using chordal graphs. The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.74,1.05)$. The matrix $Y$ is given by
\begin{equation*}
	Y(q)=\begin{bmatrix}
	\overline{Y}(q_1)&0_{2\times1}&0_{2\times1}&0_{2\times1}\\
	0_{2\times1}&\overline{Y}(q_2)&0_{2\times1}&0_{2\times1}\\
	0_{2\times1}&0_{2\times1}&\overline{Y}(q_3)&0_{2\times1}\\
	0_{2\times1}&0_{2\times1}&0_{2\times1}&\overline{Y}(q_4)
	\end{bmatrix}\;,
\end{equation*}
where $\overline{Y}(q_i)=-\begin{bmatrix}2.0125y_i,&3.2+2.3(x_i^2+y_i^2)\end{bmatrix}$.

\mypara In the unconstrained case, the solver took 9.8s to solve the MI~\eqref{eq:MI formulation} using chordal graphs. The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.69,1.24)$. The matrix $Y$ is given by
\begin{equation*}
	Y(q)=\begin{bmatrix}
	\overline{Y}_1(q)&0_{2\times1}&0_{2\times1}&0_{2\times1}\\
	0_{2\times1}&\overline{Y}_2(q)&0_{2\times1}&0_{2\times1}\\
	0_{2\times1}&0_{2\times1}&\overline{Y}_3(q)&0_{2\times1}\\
	0_{2\times1}&0_{2\times1}&0_{2\times1}&\overline{Y}_4(q)
	\end{bmatrix}\;,
\end{equation*}
where $\overline{Y}_i(q)=-\begin{bmatrix}2.38y_i,&2.88+\sum_{j=1}^4(x_j^2+y_j^2)\end{bmatrix}$
